Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-23 analysis/paper/paper.Rmd
Move workflow description to introduction

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
```

@@

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
```

>>>>

In this paper we will assume that a general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, writing the manuscript and depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).

@@

@@

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
```

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
```
